Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Add mixing

@@

		Now we have $D_{ij}^{ab}t_{ij}^{ab} = g(u, \tau)$. 
		This allows us to define an iterative scheme,
		\begin{equation}
			\tau^{(k + 1)} = \frac{g(u, \tau^{(k)})}{D_{ij}^{ab}},
		\end{equation}
		with the initial guess
		\begin{equation}
			\tau^{(0)} = \frac{u_{ij}^{ab}}{D_{ij}^{ab}}.
		\end{equation}

@@

   \section{Implmentation}
        We have costructed a flexible framework for making performing CCD computations,
        consisting of package for \lstinline{python} that is easy to install globally on any 
        computer.

@@

>>>>

\usepackage{fontspec}
\newfontfamily\DejaSans{DejaVu Sans}

\newcommand{\nan}{\DejaSans 😱}

@@

		Now we have $D_{ij}^{ab}t_{ij}^{ab} = g(u, \tau)$. 
		This allows us to define an iterative scheme,
		\begin{equation}
			\tau^{(k + 1)} = \frac{g(u, \tau^{(k)})}{D_{ij}^{ab}},
            \label{eq:iterative_amplitude}
		\end{equation}
		with the initial guess
		\begin{equation}
			\tau^{(0)} = \frac{u_{ij}^{ab}}{D_{ij}^{ab}}.
		\end{equation}

@@

\section{Implementation}
    We have costructed a flexible framework for making performing CCD
    computations, consisting of package for \lstinline{python} that is easy
    to install globally on any computer.

@@

    \subsection{Mixing}
        A way to try ``massage'' convergence out of the CCD-method is to use
        \emph{mixing}. A popular solution is Pulay mixing\footnote{Commonly
        known as DIIS (direct inversion in the iterative subspace).}. We did not
        implement Pulay mixing but used a more naïve and simpler solution.
        \begin{align}
            \tilde{t}^{k + 1} = \theta t^{k + 1} + (1 - \theta)t^k,
        \end{align}
        where $t^{k + 1}$ is the current value computed using
        \autoref{eq:iterative_amplitude} and $t^k$ is the previous value for the
        amplitude. Choosing $\theta \in [0, 1]$ we can tune how much of the
        previous amplitude we wish to include in the new state. This allows for
        a more gradual transition between the iterations. We now use
        $\tilde{t}^{k + 1}$ as our estimate of the new amplitude.

\section{Results}

    \begin{table}
        \centering
        \caption{N = 2}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}        
    \end{table}

    \begin{table}
        \centering
        \caption{N = 6}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N6}        
    \end{table}

    \begin{table}
        \centering
        \caption{Here we look at $N = 12$ particles ($R = 3$ shells).}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                      & $3$ & $46.361130$ & $46.361130$ & $46.361130$ \\
                      & $4$ & $43.663266$ & $45.837079$ & $43.309845$ \\
                      & $5$ & $41.108850$ & $45.456882$ & $40.654709$ \\
                      & $6$ & $40.750512$ & \nan & $40.068340$ \\
                $0.5$ & $7$ & $40.302718$ & \nan & $39.508500$ \\
                      & $8$ & $40.263751$ & \nan & $39.399128$ \\
                      & $9$ & $40.216688$ & \nan & $39.329310$ \\
                      & $10$ & $40.216251$ & \nan & $39.309409$ \\
                      & $11$ & $40.216194$ & \nan & $39.296007$ \\
                      & $12$ & $40.216165$ & \nan & $39.285968$ \\
                \hline
                      & $3$ & $73.765549$ & $73.765549$ & $73.765549$ \\
                      & $4$ & $70.673849$ & $73.314476$ & $70.324250$ \\
                      & $5$ & $67.569930$ & $72.990679$ & $67.031096$ \\
                      & $6$ & $67.296869$ & \nan & $66.526677$ \\
                $1.0$ & $7$ & $66.934744$ & \nan & $66.049564$ \\
                      & $8$ & $66.923094$ & \nan & $65.972157$ \\
                      & $9$ & $66.912244$ & \nan & $65.921204$ \\
                      & $10$ & $66.912035$ & \nan & $65.889281$ \\
                      & $11$ & $66.911364$ & \nan & $65.866715$ \\
                      & $12$ & $66.911364$ & \nan & $65.849775$ \\
                \hline
                      & $3$ & $120.722260$ & $120.722260$ & $120.722260$ \\
                      & $4$ & $117.339641$ & $120.299999$ & $116.995036$ \\
                      & $5$ & $113.660396$ & $120.012284$ & $113.048934$ \\
                      & $6$ & $113.484866$ & $119.872007$ & $112.658821$ \\
                $2.0$ & $7$ & $113.247601$ & $119.662201$ & $112.309482$ \\
                      & $8$ & $113.246578$ & $119.584733$ & $112.235521$ \\
                      & $9$ & $113.246302$ & $119.524417$ & $112.181828$ \\
                      & $10$ & $113.245854$ & $119.472283$ & $112.140661$ \\
                      & $11$ & $113.245255$ & $119.430435$ & $112.109972$ \\
                      & $12$ & $113.245183$ & $119.394712$ & $112.085683$
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N12}        
    \end{table}

    \begin{table}
        \centering
        \caption{N = 20}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N20}        
    \end{table}
